Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-04-05 modeling-volunteer-computing-gecco.tex
Adding loggly graph

During and after the experiment, the data can be collected from one of
the logs: the server log file, data files (that cannot be used in
Heroku, for instance)  or from online logging services such as
Loggly (\url{http://loggly.com}), which is the one we are using. Loggly was chosen for its
easiness and support from the {\tt winston} logging library; however,
it is only free for a month, so a more sustainable alternative (read:
free) will have to be sought in the future, after this paper is finished. Other online logging
services have a free tier that can be used for ever; however, its
support and graphing facilities were not so complete. Choosing a good logging
service for experiments in open science is, for us, an open issue but it is
outside the scope of this paper. It will have to be left for future
work. 
% Include loggly graphs here.
As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/splash-volunteer}. 
will be analyzed in the next section.

>>>>

During and after the experiment, the data can be collected from one of
the logs: the server log file, data files (that cannot be used in
Heroku, for instance)  or from online logging services such as
Loggly (\url{http://loggly.com}), which is the one we are using. Loggly was chosen for its
easiness and support from the {\tt winston} logging library as well as
its graphing capabilities, shown in Figure \ref{fig:loggly}; however,
it is only free for a month, so a more sustainable alternative (read:
free and open source) will have to be sought in the future, after this paper is finished. Other online logging
services have a free tier that can be used for ever; however, its
support and graphing facilities were not so complete. Choosing a good logging
service for experiments in open science is, for us, an open issue but it is
outside the scope of this paper. It will have to be left for future
work.
%
\begin{figure*}[htb]
        \centering
        \includegraphics[width=0.9\linewidth]{img/loggly.png}
        \caption{Loggly dashboard showing the evolution of fitness for
        the last 10 minutes of an experiment.}\label{fig:loggly}
\end{figure*}

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/splash-volunteer}. 
will be analyzed in the next section.
